### 2019-04-05 7_conclusion.tex
Edit conclusion.

Parameterized benchmarks are a promising new route for evaluating the
performance of parallel and distributed programming systems. By
composing a small number of orthogonal primitives, parameterized
benchmarks make it possible to explore a space of application
scenarios, while minimizing the marginal cost of developing each
additional feature. In the case of Task Bench, this has enabled a
comprehensive comparative study of programming system performance
which is unique in both the breadth of systems considered and the
depth of insight achieved about them.

Our study has both confirmed and challenged our intuitions. We have
found, unsurprisingly, that systems intended primarily for scientific
simulation are optimized for smaller task granularities than systems
for large-scale data analysis. The baseline overhead of these systems
spans over 5 orders of magnitude. Even among systems intended for HPC
there is easily 2 orders of magnitude in variation. The gap shrinks
with node count, as the most efficient systems are the most impacted
by increasing communication latencies, and also with numbers of
dependencies and with increasing task parallelism. In certain cases,
such as when task parallelism is available and compute is balanced
with communication, asynchronous systems show a substantial benefit.

>>>>

Task Bench is a promising new approach for evaluating the performance
of parallel and distributed programming systems. We have seen that
systems with support for asynchronous (and/or task-based) programming
appear to show benefits with more complicated dependency patterns,
higher node counts (because of higher communication latencies) and
more communication (because of ability to overlap it with
computation). However, all these benefits can be eclipsed if baseline
runtime overheads are too high. The current generation of task-based
systems (PaRSEC, Realm, Regent, and StarPU) show higher overheads
than traditional HPC systems, indicating that there continues to be
work to be done in this area.
